Measuring Software Ticket Quality using Statistical Analysis

### 2017-12-18 proposal/mprop.tex
Add papers between brackets on proposal summary at the top

Software engineering, compared to other engineering fields, such as
mechanical or electrical engineering, is much more abstract \citep{brooks1995mythical}- while 
performing maintenance on a car engine or on an electric panel,
you can actually touch the components, they are physical. However, in
computer science and the engineering of software, you cannot see the whole picture.
Of course one can actually open up a laptop or PC and see and touch the
components, but the software, what is actually displayed to the user, 
is a multitude of layers on top of each other: it starts with a number of characters in some file;
then, that file gets compiled or interpreted to machine
code by other components which run on the operating system; then, these components
can communicate with the kernel (i.e. the component that sits exactly
between the OS and the hardware) and eventually perform the final step - send 
different 1s and 0s encoded into electrical signals to the CPU and various
other hardware components.

@@

Firstly, we will deal with a large volume of tickets and information extracted 
from software projects and the tools that revolve around them, such as issue 
trackers and version control systems. Thus, \emph{data quality} is an important 
topic that needed to be explored in order to infer appropriate conclusions.

@@

Secondly, probably the topic of most interest to our research is \emph{issue quality}.
This field is mainly concerned with software tickets and their characteristics: how
important are issue trackers to a software project, what makes for a good bug report,
what impact does bad triaging have etc. As we are interested in finding out what
features are most important in improving the quality of a ticket, the issue quality
literature reviewed proved to be beneficial and provided valuable insight into
how other researchers tried to approach this problem.

The third topic was waste and its impact on software projects. We needed to
look into various communication and tool-related waste in software projects because
having a project with a considerable amount of waste might affect our results and
compromise the evaluation process. We investigated researches that looked into what
the main types of waste are and how it can be avoided so that
we could apply the findings into selecting the projects.

>>>>

Software engineering, compared to other engineering fields, such as
mechanical or electrical engineering, is much more abstract \citep{brooks1995mythical}- while 
performing maintenance on a car engine or on an electric panel,
you can actually touch the components, they are physical. However, in
computer science and the engineering of software, you cannot see the whole picture.
Of course one can actually open up a laptop or PC and see and touch the
components, but the software, what is actually displayed to the user, 
is a multitude of layers on top of each other: it starts with a number of characters in some file;
then, that file gets compiled or interpreted to machine
code by other components which run on the operating system; then, these components
can communicate with the kernel (i.e. the component that sits exactly
between the OS and the hardware) and eventually, after several other layers, 
perform the final step - send different 1s and 0s encoded into electrical signals 
to the CPU and various other hardware components.

@@

Firstly, we will deal with a large volume of tickets and information extracted 
from software projects and the tools that revolve around them, such as issue 
trackers and version control systems. Thus, \emph{data quality} (\cite{bachmann2009software}, 
\cite{strong1997data}, \cite{kitchenham1996software},
\cite{stamelos2002code}, \cite{lee2002aimq}, \cite{Heinrich2007MetricsDataQuality},
\cite{nelson2005antecedents}, \cite{pipino2002data}, \cite{wang1998product},
\cite{prybutok2008evaluating}, \cite{gorla2010organizational}, \cite{swanson1997maintaining},
\cite{redman1998impact}, \cite{lee2003knowing}) is an important topic that needed to be explored in order to infer 
appropriate conclusions.

@@

Secondly, probably the topic of most interest to our research is \emph{issue quality}
(\cite{bettenburg2008makes}, \cite{hooimeijer2007modeling}, \cite{schroter2010stack},
\cite{bettenburg2008extracting}, \cite{bettenburg2007quality}, \cite{bettenburg2008duplicate},
\cite{bettenburg2012using}, \cite{kim2013should}, \cite{rastkar2010summarizing}, 
\cite{zhou2012should}, \cite{fischer2003analyzing}, \cite{just2008towards}, 
\cite{anvik2006automating}, \cite{anvik2011reducing}, \cite{anvik2006should}, 
\cite{jeong2009improving}, \cite{Naguib2013BugReportAssignee}, \cite{lamkanfi2010predicting})
This field is mainly concerned with software tickets and their characteristics: how
important are issue trackers to a software project, what makes for a good bug report,
what impact does bad triaging have etc. As we are interested in finding out what
features are most important in improving the quality of a ticket, the issue quality
literature reviewed proved to be beneficial and provided valuable insight into
how other researchers tried to approach this problem.

The third topic was \emph{waste} (\cite{sedano2017software}, \cite{Korkala2014WasteIdentification},
\cite{ikonen2010exploring}, \cite{aranda2009secret}, \cite{grimstad2006framework},
\cite{harter2000effects}, \cite{turney2002thumbs}, \cite{wilson2005recognizing}) and its impact on software projects. We needed to
look into various communication and tool-related waste in software projects because
having a project with a considerable amount of waste might affect our results and
compromise the evaluation process. We investigated researches that looked into what
the main types of waste are and how it can be avoided so that
we could apply the findings into selecting the projects.
